---
title: "Create or Update Dataset"
author: "Aaron Schroeder"
date: "11/18/2021"
output: html_document
dataset:
  citation:
      title: "Social Data Commons: Education & Training: Virginia SOL Scores"
      subtitle: ""
      dsDescriptionValue: "Virginia Standards of Learning Test Scores collected by the Virginia Department of Education (VDOE)"
      dsDescriptionDate: "2021-11-17"
      timePeriodCoveredStart: "2015-01-01"
      timePeriodCoveredEnd: "2021-01-01"
      dateofCollectionStart: "2021-10-31"
      dataSources:
        - "ACS"
        - "County Health Rankings"
      author:
        - authorName: "Schroeder, Aaron"
          authorAffiliation: "Univeristy of Virginia"
        - authorName: "Charankevich, Hanna"
          authorAffiliation: "Univeristy of Virginia"
        - authorName: "Niagra, Bob"
          authorAffiliation: "Univeristy of Waterloo"
      datasetContact:
        - datasetContactEmail: "ads7fg@virginia.edu"
          datasetContactName: "Schroeder, Aaron"
  geospatial:
    geographicCoverage:
      country: "United States"
      state: "Virginia"
    geographicUnit:
      - "State Health District"
      - "County"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load dataset json template and dataset yml

```{r}
dataset_metadata <- jsonlite::read_json("dataset-metadata.json")
yml_metadata <- rmarkdown::yaml_front_matter(here::here("data-raw/dataset_create.Rmd"))
```

# Set title

```{r}
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[1]]$value <- yml_metadata$dataset$citation$title
```

# Set subtitle

```{r}
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[2]]$value <- yml_metadata$dataset$citation$subtitle
```

# Set description

```{r}
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[5]]$value[[1]]$dsDescriptionValue$value <- yml_metadata$dataset$citation$dsDescriptionValue
```

# Set description date (date of upload to dataverse)

```{r}
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[5]]$value[[1]]$dsDescriptionDate$value <- yml_metadata$dataset$citation$dsDescriptionDate
```

# Set Time period covered start date

```{r}
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[6]]$value[[1]]$timePeriodCoveredStart$value <- yml_metadata$dataset$citation$timePeriodCoveredStart
```

# Set Time period covered end date

```{r}
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[6]]$value[[1]]$timePeriodCoveredEnd$value <- yml_metadata$dataset$citation$timePeriodCoveredEnd
```

# Set Date of Collection Start (Access date)

```{r}
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[7]]$value[[1]]$dateOfCollectionStart$value <- yml_metadata$dataset$citation$dateOfCollectionStart
```

# Set data sources

```{r}
## Remove existing data source entries
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[8]]$value <- NULL
## Add data source entries
data_source_l <- as.list(yml_metadata$dataset$citation$dataSources)
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[8]]$value <- data_source_l
```

# Set authors

```{r}
## Remove existing author entries
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[3]]$value <- NULL
## Add author entries
num_yml_authors <- length(yml_metadata$dataset$citation$author)
for (i in 1:num_yml_authors) {
  dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[3]]$value[[i]] <-
    list(
      authorName = list(
        value = yml_metadata$dataset$citation$author[[i]]$authorName,
        typeClass = "primitive",
        multiple = FALSE,
        typeName = "authorName"
      ),
      authorAffiliation = list(
        value = yml_metadata$dataset$citation$author[[i]]$authorAffiliation,
        typeClass = "primitive",
        multiple = FALSE,
        typeName = "authorAffiliation"
      )
    )
}
```

# Set contact

```{r}
## Remove existing contact entries
dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[4]]$value <- NULL
## Add contact entries
num_yml_contacts <- length(yml_metadata$dataset$citation$datasetContact)
for (i in 1:num_yml_contacts) {
  dataset_metadata$datasetVersion$metadataBlocks$citation$fields[[4]]$value[[i]] <-
    list(
      datasetContactName = list(
        value = yml_metadata$dataset$citation$datasetContact[[i]]$datasetContactName,
        typeClass = "primitive",
        multiple = FALSE,
        typeName = "datasetContactName"
      ),
      datasetContactEmail = list(
        value = yml_metadata$dataset$citation$datasetContact[[i]]$datasetContactEmail,
        typeClass = "primitive",
        multiple = FALSE,
        typeName = "datasetContactEmail"
      )
    )
}
```

# Set geographic coverage

```{r}
## Remove existing geographic coverage entries
dataset_metadata$datasetVersion$metadataBlocks$geospatial$fields[[1]]$value <- NULL
## Add geographic coverage entries
nms <- names(yml_metadata$dataset$geospatial$geographicCoverage)

if ("country" %in% nms) {
  dataset_metadata$datasetVersion$metadataBlocks$geospatial$fields[[1]]$value[[1]]$country <-
    list(
      typeName = "country",
      multiple = FALSE,
      typeClass = "controlledVocabulary",
      value = yml_metadata$dataset$geospatial$geographicCoverage$country
    )
}
if ("state" %in% nms) {
  dataset_metadata$datasetVersion$metadataBlocks$geospatial$fields[[1]]$value[[1]]$state <- 
    list(
      typeName = "state",
      multiple = FALSE,
      typeClass = "primitive",
      value = yml_metadata$dataset$geospatial$geographicCoverage$state
  )
}
if ("city" %in% nms) {
  dataset_metadata$datasetVersion$metadataBlocks$geospatial$fields[[1]]$value[[1]]$city <- 
    list(
      typeName = "city",
      multiple = FALSE,
      typeClass = "primitive",
      value = yml_metadata$dataset$geospatial$geographicCoverage$city
  )
}
if ("otherGeographicCoverage" %in% nms) {
  dataset_metadata$datasetVersion$metadataBlocks$geospatial$fields[[1]]$value[[1]]$otherGeographicCoverage <- 
    list(
      typeName = "otherGeographicCoverage",
      multiple = FALSE,
      typeClass = "primitive",
      value = yml_metadata$dataset$geospatial$geographicCoverage$otherGeographicCoverage
  )
}
```

# Set geographic unit

```{r}
## Remove existing geographic unit entries
dataset_metadata$datasetVersion$metadataBlocks$geospatial$fields[[2]]$value <- NULL
## Add geographic unit entries
geo_unit_l <- as.list(yml_metadata$dataset$geospatial$geographicUnit)
dataset_metadata$datasetVersion$metadataBlocks$geospatial$fields[[2]]$value <- geo_unit_l
```

# Create or update dataverse dataset

```{r}
if (exists("data/dataset_doi")) {
  dataset_doi <- readLines(here::here("data/dataset_doi"))[1]
 
  if (is.na(dataset_doi)) {
    ## Create dataset
    ds_info <- dataverse::create_dataset(
      dataverse = "biocomplexity",
      body = dataset_metadata,
      key = Sys.getenv("DATAVERSE_KEY"),
      server = Sys.getenv("DATAVERSE_SERVER")
    )
  
    ## Save dataset DOI to data
    writeLines(ds_info$data$persistentId, here::here("data/dataset_doi"))
  } else {
    dataverse::update_dataset(
      dataset = dataset_doi,
      body = dataset_metadata,
      key = Sys.getenv("DATAVERSE_KEY"),
      server = Sys.getenv("DATAVERSE_SERVER")
    )
  }
}



```
